---
title: "Robust Variable Selection with Exponential Squared Loss"
author: "Borui Tang, Jin Zhu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Robust Variable Selection with Exponential Squared Loss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of rvs is to carry out robust variable selection through exponential sqared loss. Specifically, it solves the following optimization problem: 

\[
argmin_{\beta} \sum_{i=1}^n(1-exp{-(y_i-x_i^T\beta)^2/\gamma_n})+n\sum_{i=1}^d p_{\lambda_{nj}(|\beta_j|)}.
\]

We use the adaptive LASSO penalty. Regularization parameters are chosen adaptively by default, while they can be supplied by the user. Block coordinate gradient descent algorithm is used to efficiently solve the optimiztion problem.

<!-- ## Installation -->

<!-- You can install the released version of rvs from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("rvs") -->
<!-- ``` -->

## Quick Start

This is a basic example which shows you how to use this package:

```{r example}
library(MASS)
library(rvs)
## basic example code

#### generate data
set.seed(1)
N <- 100
p <- 8
rho <- 0.2
mu <- rep(0, p)
Sigma <- rho * outer(rep(1, p), rep(1, p)) + (1 - rho) * diag(p)
ind <- 1:p
beta <- (-1)^ind * exp(-2 * (ind - 1) / 20)
lambda_seq <- seq(0.05, 5, length.out = 100)
X <- mvrnorm(N, mu, Sigma)
Z <- rnorm(N, 0, 1)
k <- sqrt(var(X %*% beta) / (3 * var(Z)))
Y <- X %*% beta + drop(k) * Z

#### apply rvs
rvs(X, Y)
```

## Boston Housing Price Dataset
We apply this package to analysis the Boston Housing Price Dataset, which is available in 'MASS' package. The data contain 14 variables medv. There are 506 observations in the dataset. The response variable is medv (median value of owneroccupied homes in thousand dollars), and the rest are the predictors. Here the predictors are scaled to have zero mean and unit variance. The responses are centerized.
```{r}
library(MASS)
data(Boston)
Boston[, -14] <- scale(Boston[, -14])
Boston[, 14] <- scale(Boston[, 14], scale = FALSE)
head(Boston)
```

```{r}
# comparison with OLS and MM estimators
set.seed(1)
x <- as.matrix(Boston[, -14])
y <- Boston[, 14]
lm_OLS <- lm(y~x-1)
beta_OLS <- lm_OLS$coefficients
rlmb <- rlm(y~x-1 , method = "MM") 
beta_MM <- rlmb$coefficients
beta_rvs <- rvs(x, y)

beta_OLS
beta_MM
beta_rvs
```








